Conference Paper Critique

### 2019-03-29 conf_paper/critique.tex
fixed the lad

The two most glaring omissions in the paper are the third oscillator design mentioned in the course of the paper yet is not analysed and the rather poor performance of Design ``1a'' (ring oscillator and clocked phase detector) which was unable to acquire lock at 5 MHz and had to be analysed at the reduced frequency of 1.25 MHz (the output of the in-circuit divider). %TODO
The third oscillator, briefly mentioned in the paper, is of the type most similar to that used by Zianbetlov/Shan in their paper, which like Oscillator 1 is made up of a counter driven by the FPGA clock. However, unlike Oscillator 1 it is linear in period rather than frequency thus making it more comparable to the ring oscillator design I used. It would make for a more appropriate comparison of designs and has greater correlation with real world usage had it been used but was not as Oscillator 1 was chosen as the clocked design early in the project.\\

>>>>

The two most glaring omissions in the paper are the third oscillator design mentioned in the course of the paper yet is not analysed and the rather poor performance of Design ``2a'' (ring oscillator and clocked phase detector) which was unable to acquire lock at 5 MHz and had to be analysed at the reduced frequency of 1.25 MHz (the output of the in-circuit divider). %TODO
The third oscillator, briefly mentioned in the paper, is of the type most similar to that used by Zianbetlov/Shan in their paper, which like Oscillator 1 is made up of a counter driven by the FPGA clock. However, unlike Oscillator 1 it is linear in period rather than frequency thus making it more comparable to the ring oscillator design I used. It would make for a more appropriate comparison of designs and has greater correlation with real world usage had it been used but was not as Oscillator 1 was chosen as the clocked design early in the project.\\
